Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-28 papers/FX/draft.tex
Revised the paper with Thomas.

>>>>

To test whether two series share the same tail index, we concatenate
the two series and apply the Hoga test. For the ``Energy'' and the
``Consumer Staples'' sector, we summarise the results in figure
\ref{fig:Hoga_Energy_pair} and \ref{fig:Hoga_consumer_Staples_pair}.
\begin{figure}[htb!]
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{Hoga_Energy_pair.pdf}
    \caption{``Energy''}
    \label{fig:Hoga_Energy_pair}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{Hoga_Consumer_Staples_pair.pdf}
    \caption{``Consumer Staples''}
    \label{fig:Hoga_consumer_Staples_pair}
  \end{subfigure}
  \caption{Hoga Test Statistics of stocks in the ``Energy'' and
    ``Consumer Staples'' sectors of
    S\&P 500. The green, blue and red colors represent, respectively,
    exceedances of the 85\%, 90\% and 95\% quantiles of the distribution of
    \eqref{eq:Q1_distr}.
    Grey points stand for pairs for which the test statistic is below
    the 85\% quantile;
    black points represent pairs for which
    computation of the test statistics fails for given precision
    requirements and time limits}.
\end{figure}
Clearly, these figures show that the null
hypothesis of an equal tail index is rejected for more pairs in the
``Energy'' sector than it is for those in the ``Consumer Staples''
sector. This suggests that lower tail indices of stocks in the
``energy'' sector are more spread out than are those of the ``Consumer
Staples'' sector.

Also observe that while 3 stocks, say A, B and C, test in favor of
relations $\alpha_A = \alpha_B, \alpha_A \neq \alpha_C$, it often
happens that another test on B and C is supportive of $\alpha_B =
\alpha_C$ . This is due to the limited power of the test. Based
on such results, one may guess $\alpha_B$ lies between $\alpha_A$ and
$\alpha_C$. The test is unable to recognize the smaller differences
between $\alpha_A, \alpha_B$ and between $\alpha_B, \alpha_C$.

To have an idea about the power of Hoga's test, we run it on
concatenated samples drawn from t-distributions with different degrees
of freedom. Figure \ref{fig:t_sim_pair} shows the result.
\begin{figure}[htb!]
  \centering
  \includegraphics[width=\textwidth]{t_sim_pair.pdf}
  \caption{Test Statistics of concatenated t-samples with different
    degrees of freedom. Numbers on the axis are the degrees of freedom.}
  \label{fig:t_sim_pair}
\end{figure}
From the figure one can see that the power of the test decreases as
the minimum tail index of a concatenated pair increases.
